---
title: "Options Homework for MFIN 820"
author: "Refik Türkeli"
date: "22/2/2019"
output: pdf_document
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(scales)
library(kableExtra)
source("analysis.R")
```

For my homework, I'm selecting Tesla, Inc. as my last name starts with T.
As of this writing, Tesla's stock price is $`r stock_price`. I have downloaded
options prices from [Yahoo Finance](https://finance.yahoo.com/quote/TSLA/options)
on `r time_of_data`. Raw data can be observed 
[here](https://github.com/refik/options-mfin820/blob/master/options-data.R).
The code written for generating this document can be seen 
[on Github](https://github.com/refik/options-mfin820).

## Q1. Confirm that higher exercise prices mean lower call prices and higher put prices.

To confirm this, option prices have been filtered. Only options that have been
traded in the last 3 hours and have a volume more than 20 are selected. 
Options used for this analysis have a maturity of 30 days. Data for this plot can be observed at the end of this report.  
  
  
```{r, echo = FALSE}
strike_effect_plot
```

\newpage

## Q2. Confirm that longer maturity means higher prices for both calls and puts.

To observe the effect of maturity, options with 15 days and 30 days to expiry
are compared. As it can be seen from the plot, in all cases the slope is positive 
for both puts and calls.

```{r, echo = FALSE}
maturity_pair %>% 
    spread(maturity, last_price) %>% 
    select(Type = type, Strike = strike_price, 
           `15 days` = `15`, `30 days` = `30`) %>% 
    kable(booktabs = TRUE, linesep = "") %>% 
    kable_styling(latex_options = "striped", position = "center")
```

```{r, echo = FALSE}
maturity_effect_plot
```

## Q3. Choose a put and call with the same exercise price and maturity. Confirm that the put-call parity holds

Risk free 1 month treasury yield curve rate observed at the time of this report
is `r percent(risk_free_30d)`. Stock price for Tesla, Inc. is $`r stock_price`. Put-call parity holds nearly perfectly.

```{r, echo = FALSE}
parity_data %>% 
    select(Strike = strike_price, C = call, P = put, 
           `PV(X)` = `pv(strike)`, `C + PV(X)` = `call + pv(strike)`,
           `P + S` = `put + spot`, Difference = `parity_difference`) %>% 
    kable(digits = 2, booktabs = TRUE, linesep = "") %>% 
    kable_styling(latex_options = "striped", position = "center")
```

\newpage

## Appendix: Data

```{r, echo = FALSE}
options %>% 
    select(Type = type, Maturity = maturity,
           `Strike Price` = strike_price, `Last Price` = last_price) %>% 
    kable(booktabs = TRUE, longtable = TRUE, linesep = "") %>% 
    kable_styling(latex_options = c("repeat_header", "striped"), position = "center")
```